A mechanization of Kan complexes in the calculus of inductive constructions

### 2022-08-16 paper/paper.tex
paper: MAJ title

\title{An indexed construction of semi-simplicial and semi-cubical types}
\author{
  \textcolor{gray80}{Ramkumar Ramachandra} \\
  \itshape \textcolor{gray80}{Université Paris-Cité}
  \and
  \textcolor{gray80}{Hugo Herbelin} \\
  \itshape \textcolor{gray80}{Institut de Recherche en Informatique Fondamentale}
}
\date{}

@@

The proof of $\cohf$ require an higher-dimensional coherence condition which we obtain by working in \texttt{HSet}. If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).

@@

  \bibitem[CohCoq]{Cohen16}
  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. \emph{arXiv preprint arXiv:1611.02108}.

>>>>

\title{A mechanization of Kan complexes in the calculus of inductive constructions}
\author{
  \textcolor{gray80}{Ramkumar Ramachandra} \\
  \itshape \textcolor{gray80}{Université Paris-Cité}
  \and
  \textcolor{gray80}{Hugo Herbelin} \\
  \itshape \textcolor{gray80}{Institut de Recherche en Informatique Fondamentale}
}
\date{}

@@

The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \texttt{HSet}. If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).

@@

  \bibitem[Takeuti–Gandy]{Barras15}
  Barras, B., Coquand, T., \& Huber, S. (2015). A generalization of the Takeuti–Gandy interpretation. \emph{Mathematical structures in computer science}, 25(5), 1071-1099.

  \bibitem[CCHM]{Cohen16}
  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. \emph{arXiv preprint arXiv:1611.02108}.
